Einschätzung zu den Befindlichkeiten der Wirtschaft in den Nachbarländern

### 2022-10-02 Paper_neighbour_countries_II.Rmd
Commit, 2.10.22

dat_hind_fac_i <- get_eurostat(id="ei_bsin_q_r2") #Industry (quarterly: ei_bsin_q_r2)
dat_hind_fac_s <- get_eurostat(id="ei_bsse_q_r2") #Services (quarterly: ei_bsin_q_r2)

d_hind_i <- filter(dat_hind_fac_i,indic ==  "BS-FLP3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01") 
d_hind_s <- filter(dat_hind_fac_s,indic =="BS-FLB3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01")

d_hind_i$time <- as.yearqtr(d_hind_i$time)
d_hind_s$time <- as.yearqtr(d_hind_s$time)

d_hind_i <- rename(d_hind_i,Industry=values)
d_hind_s <- rename(d_hind_s,Services=values)

d_hind_i <- d_hind_i %>% 
  select(time, geo, Industry)
d_hind_s <- d_hind_s %>% 
  select(time, geo, Services)

d_hind_both <- merge(d_hind_i,d_hind_s,by=c("time","geo"),all=TRUE)

d_hind_both <- pivot_longer(d_hind_both, cols = 3:4, names_to ="branches",
 values_to = "values")

@@

d_hind_both$branches[d_hind_both$branches=="Industry"] <- "Industrie"
d_hind_both$branches[d_hind_both$branches=="Services"] <- "Dienstleistungen"

@@

d <- filter(dat_hind,indic =="BS-FLBA4-PC", geo %in% cat, s_adj == "SA",time>="2019-01-01")

d$indic[d$indic=="BS-FLBA4-PC"] <- "Arbeitskräftemangel"

p <- ggplot(data = d) + 
    geom_line(mapping = aes(x = time, y = values),size=.6) + 
    scale_color_manual(values = c("#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=.2) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
 # scale_x_date(date_labels = "%YQ%q",breaks=break.vec) +
 # zoo::scale_x_yearqtr(limits = c(min(d_hind_s$time), max(d_hind_s$time)),format = '%Y Q%q')+
  scale_x_date(date_labels = "%b %y",breaks=break.vec) +
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +   #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hind_constr.pdf')
print(p)
dev.off()

>>>>

dat_hind_fac_i <- get_eurostat(id="ei_bsin_q_r2") #Industry (quarterly: ei_bsin_q_r2)
dat_hind_fac_s <- get_eurostat(id="ei_bsse_q_r2") #Services (quarterly: ei_bsin_q_r2)
dat_hind_constr <- get_eurostat(id="ei_bsbu_m_r2") #construction monthly

d_hind_i <- filter(dat_hind_fac_i,indic ==  "BS-FLP3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01") 
d_hind_s <- filter(dat_hind_fac_s,indic =="BS-FLB3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01")
d_hind_c <- filter(dat_hind_constr,indic =="BS-FLBA4-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01")

d_hind_i$time <- as.yearqtr(d_hind_i$time)
d_hind_s$time <- as.yearqtr(d_hind_s$time)
d_hind_c <- d_hind_c %>%
  group_by(geo,time = paste(lubridate::year(time),quarters(time))) %>%
  summarise(values = mean(values)) %>% 
  ungroup()
d_hind_con <- select(d_hind_c,time,geo,values)
d_hind_con <- arrange(d_hind_con,desc(time))
d_hind_con$time <- as.yearqtr(d_hind_con$time)

d_hind_i <- rename(d_hind_i,Industry=values)
d_hind_s <- rename(d_hind_s,Services=values)
d_hind_con <- rename(d_hind_con,Construction=values)

d_hind_i <- d_hind_i %>% 
  select(time, geo, Industry)
d_hind_s <- d_hind_s %>% 
  select(time, geo, Services)
d_hind_con <- d_hind_con %>% 
  select(time, geo, Construction)

d_hind_both <- merge(d_hind_i,d_hind_s,by=c("time","geo"),all=TRUE)
d_hind_both <- merge(d_hind_both,d_hind_con,by=c("time","geo"),all=TRUE)

d_hind_both <- pivot_longer(d_hind_both, cols = 3:5, names_to ="branches",
 values_to = "values")

@@

d_hind_both$branches[d_hind_both$branches=="Industry"] <- "Industrie"
d_hind_both$branches[d_hind_both$branches=="Services"] <- "Dienstleistungen"
d_hind_both$branches[d_hind_both$branches=="Construction"] <- "Baugewerbe"

@@

d <- filter(dat_hind,indic =="BS-FLBA4-PC", geo %in% cat, s_adj == "SA",time>="2019-03-01")

a <- d %>%
  group_by(geo,quarter = paste(lubridate::year(time),quarters(time))) %>%
  summarise(values = mean(values)) %>% 
  ungroup()
b <- select(a,quarter,geo,values)
b <- arrange(b,desc(quarter))

b$quarter <- as.yearqtr(b$quarter)

#b <- data.frame(apply(b,2,unclass))

b$geo[b$geo=="AT"] <- "Österreich"
b$geo[b$geo=="EA19"] <- "EU-19"
b$geo[b$geo=="DE"] <- "Deutschland"
b$geo[b$geo=="FR"] <- "Frankreich"
b$geo[b$geo=="IT"] <- "Italien"

#d$indic[d$indic=="BS-FLBA4-PC"] <- "Arbeitskräftemangel"

break.vec <- c(seq(from = min(d$time), to = max(d$time),
                   by = "24 month"),max(d$time))

p <- ggplot(data = b) + 
    geom_line(mapping = aes(x = quarter, y = values,color=geo),size=.6) + 
    scale_color_manual(values = c("#8E44AD","#ffa500","#659065","#A0522D","red")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=.2) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
 # scale_x_date(date_labels = "%YQ%q",breaks=break.vec) +
 # zoo::scale_x_yearqtr(limits = c(min(d_hind_s$time), max(d_hind_s$time)),format = '%Y Q%q')+
    zoo::scale_x_yearqtr(breaks = seq(from = min(b$quarter), to = max(b$quarter), by = 2),format = '%Y Q%q')+
    theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +   #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hind_constr_q.pdf')
print(p)
dev.off()
